On Adding Pattern Matching to Haskell-based Deeply Embedded Domain Specific Languages\\ \large{Not For Distribution}

### 2020-07-20 paper/paper.tex
Work on abstract

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  %Say what problem is
  The data flow in deeply embedded domain specific langauges  falls out naturally.

  Capturing control flow in embbed
  is critical for 
  Using a deep embedding of 
 Programs that write programs 
  Sometimes,  
Embedded Domain Specific Languages are the killer app of functional languages.
%Say why it is an interesting problem
Languages with reification of code fragments allows
for high-level abstractions that directly support
diverse applications incuding machine learning and hardware description generation.
% 
  Haskell in particual has been used for many embeded code generators, such
as Lava, SunRoof, Conal work, CCC, AD, ... (finally tagless) diagrams?
%Say what our solution achieves
In this paper, we expand the capabilies of traditional,
Haskell-based, deep embeddings with a compiler extension
for capturing the useful abstraction of pattern matching. 
%Here is why the world will be a better place
With this new support, the Haskell that we capture for expressing
embededed-based solutions can be cleaner, more Haskell idiomatic,
and more declaritive in nature.

>>>>

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  %Say what problem is

  Capturing control flow in an embedded domain specific language is crucial for
  writing programs in a "natural" style. This enables the programmer to use the
  constructs that are already builtin to the base language, such as pattern
  matching and recursion.

  In addition to control flow, when these features are reified, the data flow in
  a deeply embedded domain specific langauge also falls out naturally.

  is critical for 
  Using a deep embedding of 
 Programs that write programs 
  Sometimes,  
Embedded Domain Specific Languages are the killer app of functional languages.

%Say why it is an interesting problem

In embedded domain specific languages which do not capture control flow
constructs, workarounds must be employed which will be less familiar
than the builtin control flow mechanisms of the host language. When
control flow mechanisms are represented in the embedded language,
a much more natural style of programming is offered to the programmer.

Languages with reification of code fragments allow
for high-level abstractions that directly support
diverse applications incuding machine learning and hardware description generation.
% 
  Haskell in particular has been used for many embedded code generators, such
  as Lava, SunRoof, Conal work, CCC, AD, ... (finally tagless) diagrams? Feldspar (note: Feldspar has some form of \ttt{switch} primitive)?

%Say what our solution achieves

In this paper, we expand the capabilies of traditional,
Haskell-based, deep embeddings with a compiler extension
for capturing the useful abstraction of pattern matching. This is accomplished
using a deeply embedded representation of the pattern match construct.

%Here is why the world will be a better place

With this new support, the Haskell that we capture for expressing
embedded-based solutions can be cleaner, more Haskell idiomatic,
and more declarative in nature.
